---
title: "Example Document with Review Extension"
author: "Quarto Review Team"
format:
  html:
    toc: true
    code-fold: true
---

# Introduction {#sec-intro}

This is an example document demonstrating the **Quarto Review
Extension**. Click on any paragraph, heading, or code block to edit it
directly in your browser.

## Features

The review extension provides several powerful features:

- **In-browser editing**: Click any element to edit with a live
  preview

- **Change tracking**: All edits are tracked as operations

- **CriticMarkup support**: Use standard markup for annotations

- **Git integration**: Save changes directly to your repository Test

## How to Use

### Editing Content

Simply click on any text element to open the editor. The editor
provides:

1.  A textarea for editing markdown
2.  Live preview of your changes
3.  Save and cancel buttons

### Using CriticMarkup

You can use CriticMarkup syntax for annotations:

-   Addition: `{++new text++}`
-   Deletion: `{--old text--}`
-   Substitution: `{~~old~>new~~}`
-   Comment: `{>>This is a comment<<}`
-   Highlight: `{==important text==}{>>with note<<}`

Here's an example with {==highlighted text==}.

## Lists

### Bullet List

-   First item
-   Second item with some {++added text++}
-   Third item

### Nested Bullet List

-   First item
-   Second item with some
-   Third item
    -   Nested item
    -   Another nested item

### Ordered List

1.  Step one
2.  Step two
3.  Step three

## Collaboration

The review extension supports multiple users with different permission
levels:

-   **Viewer**: Can view and comment
-   **Editor**: Can view, comment, and edit
-   **Admin**: Full access including merge permissions

## Technical Details

### Architecture

The extension uses a modular architecture:

-   **Changes Module**: Tracks operations in-memory
-   **Markdown Module**: Converts markdown to HTML
-   **Comments Module**: Handles CriticMarkup annotations
-   **Git Module**: Provides version control integration
-   **UI Module**: Stateless rendering layer

```{r}
print("Some code that is not editable.")
```

### Git Providers

The extension supports multiple git providers:

| Provider | Support |
|----------|---------|
| GitHub   | ✅      |
| GitLab   | ✅      |
| Gitea    | ✅      |
| Forgejo  | ✅      |
| Local    | ✅      |

More text

```{r}
#| label: fig-cars
#| fig-cap: "A caption for a figure should be editable"
plot(cars)
```

A caption for a figure should be editable

## Conclusion

This example demonstrates the capabilities of the Quarto Review
Extension. Try clicking on different elements to see the editing
functionality in action!

::: {#quarto-navigation-envelope .hidden}
::: {data-review-markdown="[Quarto Review Example]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1zaWRlYmFyLXRpdGxl&quot;} [Quarto Review
Example]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1uYXZiYXItdGl0bGU=&quot;} [Home]{.hidden
.quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1uYXZiYXI6SG9tZQ==&quot;} [/document.html]{.hidden
.quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1uYXZiYXI6L2RvY3VtZW50Lmh0bWw=&quot;}
[Debug]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1uYXZiYXI6RGVidWc=&quot;}
[/debug-example.html]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1uYXZiYXI6L2RlYnVnLWV4YW1wbGUuaHRtbA==&quot;}
[Translation]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1uYXZiYXI6VHJhbnNsYXRpb24=&quot;}
[/doc-translation.html]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLWludC1uYXZiYXI6L2RvYy10cmFuc2xhdGlvbi5odG1s&quot;}" class="review-editable" data-review-id="home-runner-work-quarto-review-extension-github-demo-quarto-review-extension-github-demo-output-document.sec-intro.conclusion.para-11" data-review-origin="source" data-review-type="Para"}
[Quarto Review Example]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1zaWRlYmFyLXRpdGxl"} [Quarto Review
Example]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1uYXZiYXItdGl0bGU="} [Home]{.hidden
.quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1uYXZiYXI6SG9tZQ=="} [/document.html]{.hidden
.quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1uYXZiYXI6L2RvY3VtZW50Lmh0bWw="}
[Debug]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1uYXZiYXI6RGVidWc="}
[/debug-example.html]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1uYXZiYXI6L2RlYnVnLWV4YW1wbGUuaHRtbA=="}
[Translation]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1uYXZiYXI6VHJhbnNsYXRpb24="}
[/doc-translation.html]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLWludC1uYXZiYXI6L2RvYy10cmFuc2xhdGlvbi5odG1s"}
:::
:::

::: {#quarto-meta-markdown .hidden}
::: {data-review-markdown="[Example Document with Review Extension -- Quarto Review
Example]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLW1ldGF0aXRsZQ==&quot;} [Example Document with Review
Extension -- Quarto Review Example]{.hidden
.quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLXR3aXR0ZXJjYXJkdGl0bGU=&quot;} [Example Document with
Review Extension -- Quarto Review Example]{.hidden
.quarto-markdown-envelope-contents render-id=&quot;cXVhcnRvLW9nY2FyZHRpdGxl&quot;}
[Quarto Review Example]{.hidden .quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLW1ldGFzaXRlbmFtZQ==&quot;} []{.hidden
.quarto-markdown-envelope-contents
render-id=&quot;cXVhcnRvLXR3aXR0ZXJjYXJkZGVzYw==&quot;} []{.hidden
.quarto-markdown-envelope-contents render-id=&quot;cXVhcnRvLW9nY2FyZGRkZXNj&quot;}" class="review-editable" data-review-id="home-runner-work-quarto-review-extension-github-demo-quarto-review-extension-github-demo-output-document.sec-intro.conclusion.para-12" data-review-origin="source" data-review-type="Para"}
[Example Document with Review Extension -- Quarto Review
Example]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLW1ldGF0aXRsZQ=="} [Example Document with Review
Extension -- Quarto Review Example]{.hidden
.quarto-markdown-envelope-contents
render-id="cXVhcnRvLXR3aXR0ZXJjYXJkdGl0bGU="} [Example Document with
Review Extension -- Quarto Review Example]{.hidden
.quarto-markdown-envelope-contents render-id="cXVhcnRvLW9nY2FyZHRpdGxl"}
[Quarto Review Example]{.hidden .quarto-markdown-envelope-contents
render-id="cXVhcnRvLW1ldGFzaXRlbmFtZQ=="} []{.hidden
.quarto-markdown-envelope-contents
render-id="cXVhcnRvLXR3aXR0ZXJjYXJkZGVzYw=="} []{.hidden
.quarto-markdown-envelope-contents render-id="cXVhcnRvLW9nY2FyZGRkZXNj"}
:::
:::